|

### 2024-04-22 manuscript.Rmd
Fixed osf download bug

  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)

@@

>>>>

  if (!file.exists('local/robotsmvpa/301_101.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='robotsmvpa.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/robotsmvpa.zip',exdir='local/',overwrite=TRUE)
  }
  if (!file.exists('local/responsedata/301trialorderRobots.mat')){
  osffiles <- osf_retrieve_file('fvsq8')
  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
  }
  comparisons <- matrix(c(1,2,1,3,2,3),nrow=3,ncol=2,byrow=TRUE)

@@

  if (!file.exists('local/masksmvpa/351_101.mat')){
  osfproject <- osf_retrieve_node('uzbns')
  osffiles <- osf_ls_files(osfproject)
  fid <- which(osffiles$name=='masksmvpa.zip')
  osf_download(osffiles[fid,], path='local/',progress=TRUE)
  unzip('local/masksmvpa.zip',exdir='local/',overwrite=TRUE)
  }
    if (!file.exists('local/responsedata/351trialorderMasks.mat')){
  osffiles <- osf_retrieve_file('fvsq8')
  osf_download(osffiles, path='local/',progress=TRUE,conflicts='overwrite')
  unzip('local/responsedata.zip',exdir='local/',overwrite=TRUE)
    }
